{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-13 paper/paper.tex
added paragraph about states

Now we come to the semantics part.

>>>>

Now we come to the semantics part. The main idea is to build a the semantics
for multithreaded programs by combining the semantics for sequential programs
with a scheduler.

All active\footnote{a thread is active from \texttt{start \textit{pc}} until
it reaches the \texttt{exit} point} threads are collected in a set $Thead$.
The state of the concurrent running threads is defined as the product of
the partial function space $(Thread \rightharpoonup LocState)$ and the set of
global memories $GMemory$. Where $LocState$ is the internal memory of a
thread, from there no information can leak and the $GMemory$ is the critical
part of the system, because it is a memory shared between all active threads.
